---
title: "viz_part1"
output: github_document
date: "2022-09-29"
---

```{r, message=F}
library(tidyverse)
library(ggridges)
```

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

## Scatterplots
Let's make a scatterplot
```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point()
```


Let's make the same scatterplot but different

```{r}
weather_scatterplot = weather_df %>% 
  drop_na() %>% 
  filter(name == "CentralPark_NY") %>% 
  ggplot(aes(x = tmin, y = tmax)) 

weather_scatterplot + 
  geom_point()
```




```{r}
ggplot(weather_df, aes(x = tmin, y = tmax)) + 
  geom_point(aes(color = name), alpha = 0.3) +
  geom_smooth(aes(color = name), se = F) + # need to put aes(color) here too, se=F removes error bar 
  facet_grid(.~name) # row ~ column stratifier
```


```{r}
ggplot(weather_df, aes(x = date, y = tmax, color = name)) + 
  geom_point(aes(size = prcp), alpha = 0.3) +
  geom_smooth( se = F) + # need to put aes(color) here too, se=F removes error bar 
  facet_grid(.~name) + 
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5))# row ~ column stratifier
```

```{r}
weather_df %>% 
  ggplot(aes(x = tmin, y = tmax)) +
  geom_hex() # see the number of data points in each area of the plot, good for large datasets
```


## Univariate plots

```{r}
weather_df %>% 
  ggplot(aes(x=tmax, fill = name)) + # not color as it is related to the border
  geom_histogram() +
  facet_grid(.~name)
```

Let's see more options

```{r}
weather_df %>% 
  ggplot(aes(x=tmax, fill = name)) + 
  geom_density(alpha = 0.3)
```

Onto boxplots

```{r}
weather_df %>% 
  ggplot(aes(x=name, y=tmax, fill=name)) + 
  geom_boxplot()
```

Violin plots give the distribution and the attributes given from a boxplot. Useful if comparing 30 things 

```{r}
weather_df %>% 
  ggplot(aes(x=name, y=tmax, fill=name)) + 
  geom_violin()
```
OR
Create each density and stacks them up next to each other - close enough for direct comparison, better than overlapping density plots for 30 things.
```{r}
weather_df %>% 
  ggplot(aes(x = tmax, y = name)) +
  geom_density_ridges()
```


## Saving and embedding plots

First, let's save a plot

```{r}
weather_scatterplot = 
  weather_df %>% 
  ggplot(aes(x = tmin, y = tmax, color = name)) +
  geom_point(aes(size = prcp), alpha = 0.3) +
  geom_smooth(se = F) +
  facet_grid(.~name)

weather_scatterplot

ggsave("./results/weather_scatterplot.pdf",weather_scatterplot, width = 8, height = 5)
  
```















